---
title: "Project Data Cleaning"
output: html_document
date: '2022-10-01'
---


```{r}
require(tidyverse)
require(ggplot2)
require(scales)
require(randomForest)
require(rpart)
require(rpart.plot)
require(factoextra)
require(corrplot)
require(ggiraphExtra)
require(jtools)
require(cowplot)
require(glmnet)

allSongs <- read.csv("Songs Data.csv")
songInfo <- read.csv("song_info.csv")

```

---
Cleaning the data to remove duplicates
---

```{r}
########### Check for total number of unique songs
length(unique(allSongs$Song))

########### Remove all duplicate songs
UniqueSongs <- allSongs %>%
  distinct(Song, .keep_all = TRUE)

########### Remove column I created for song length in seconds
UniqueSongs <- UniqueSongs %>% 
  select(!Song_Duration.Sec.)

########### Change song length from milliseconds to seconds and remove milliseconds and time signature columns
UniqueSongs <- UniqueSongs %>% 
  mutate(Length_Sec = song_duration_ms / 1000) %>% 
  select(!c(song_duration_ms, Time_Signature))
 
########### Check for duplicates in clean data
length(unique(UniqueSongs$Song))
sum(duplicated(UniqueSongs$Song))

# Check for NAs -- No NAs
colSums(is.na(UniqueSongs))

```


```{r}
######################### SONG INFO
songInfo

```

---
Assigning genres to the songs based on playlist
---
```{r}
######################### JOIN THE TABLES
songInfo <- songInfo %>% 
  rename(Song = song_name)


completeTable <- UniqueSongs %>% 
  inner_join(songInfo, by = "Song")

##### Assign genres to the songs based on the playlists the songs came from
completeTable$Genre <- case_when(
                                grepl("Alternative", completeTable$playlist) ~ "Alternative",
                                grepl("Rock", completeTable$playlist) ~ "Rock",
                                grepl("Hip Hop", completeTable$playlist) |
                                  grepl("Hip-Hop", completeTable$playlist) ~ "Hip Hop",
                                grepl("Pop", completeTable$playlist) ~ "Pop",
                                grepl("Country", completeTable$playlist) ~ "Country",
                                grepl("Latin", completeTable$playlist) | 
                                  grepl("Abuela", completeTable$playlist) ~ "Latin"
                                )

########### Remove all duplicate songs
completeTable <- completeTable %>%
  distinct(Song, .keep_all = TRUE)

completeTable %>% 
  group_by(Genre) %>% 
  count()

data <- completeTable %>% 
  drop_na() 

data <- data %>%
  distinct(Song, .keep_all = TRUE) 

aggregate(data$Song, list(data$Genre), FUN=length)

```


---
Separating the data into genres
---
```{r}
######## Creating subsets by Genre


### Alternative
AlternativeData <- data %>%
  filter(Genre == "Alternative") %>% 
  select(!c(Song, artist_name, album_names, playlist, Genre))

### Country
CountryData <- data %>%
  filter(Genre == "Country") %>% 
  select(!c(Song, artist_name, album_names, playlist, Genre))

### Hip_Hop
Hip_HopData <- data %>%
  filter(Genre == "Hip Hop") %>% 
  select(!c(Song, artist_name, album_names, playlist, Genre))

### Latin
LatinData <- data %>%
  filter(Genre == "Latin") %>% 
  select(!c(Song, artist_name, album_names, playlist, Genre))

### Pop
PopData <- data %>%
  filter(Genre == "Pop") %>% 
  select(!c(Song, artist_name, album_names, playlist, Genre))

### Rock
RockData <- data %>%
  filter(Genre == "Rock") %>% 
  select(!c(Song, artist_name, album_names, playlist, Genre))

```



---
Exploratory Data Analysis
---

```{r}

##########################################  
# Subseting the data for Visualizations
##########################################
corr_data = subset(data, select = -c(Song, artist_name, album_names, playlist))

genre_list = unique(corr_data$Genre)
genre_list

length(genre_list)

########################################
# Here, we are showing the correlations between each song attribute, seperated by Genre
########################################

par(mfrow=c(2,3))

for (g in genre_list)
  {
 corrplot(cor( subset(corr_data[corr_data$Genre == g,], select = -c(Genre)) ),
         method = 'square',
         addCoef.col = 1,
         number.cex = 0.5,
         tl.cex = 0.5,
         title = g,
         mar=c(0,0,1,0)) 
}

########################################
#These plots show the density distributions of Danceability, Energy and Popularity for all songs across all genres
########################################

{
####### Density of danceabilty for all genres
plot1 <- ggplot(corr_data, aes(x=Danceability)) + 
  geom_histogram(aes(y=..density..), color="black", fill="white", bins = 50)+
  geom_density(alpha=.2, fill="red") +
  labs(title = "Danceability Densities For All Genres")

####### Density of Energy for all genres
plot2 <- ggplot(corr_data, aes(x=Energy)) + 
  geom_histogram(aes(y=..density..), color="black", fill="white", bins = 50)+
  geom_density(alpha=.2, fill="yellow") +
  labs(title = "Energy Densities For All Genres")

####### Density of Popularity for all genres
plot3 <- ggplot(corr_data, aes(x=Popularity)) + 
  geom_histogram(aes(y=..density..), color="black", fill="white", bins = 50)+
  geom_density(alpha=.2, fill="green") +
  labs(title = "Popularity Densities For All Genres")


plot_grid(plot1, plot2, plot3, labels = "AUTO")
}


######################################## 
# Here we have the distributions of danceability and energy scores in boxplots, seperated by Genre
########################################

{
####### Boxplot for energy distributions by genre
box1 <- ggplot(corr_data, aes(x=Genre,y=Energy, fill=Genre)) +
  geom_boxplot() +
  labs(title = "Energy Scores by Genre") +
  theme(legend.position="none")


####### Boxplot for danceability distributions by genre
box2 <- ggplot(corr_data, aes(x=Genre,y=Danceability, fill = Genre)) +
  geom_boxplot() +
  labs(title = "Danceability Scores by Genre") +
  theme(legend.position="none")

plot_grid(box1, box2, labels = "AUTO")
}


```


---
LASSO
Here, we use Lasso to help us determine whatvariabeshave the greatest contribution to the model of predicting Popularity 

We find that the top two most impactful variables for predicting Popularity among all the songs in all genres are Danceability and Energy
---

```{r}
#### All Genres Lasso to find most important Variables
set.seed(1)
x = model.matrix(Popularity ~ ., data=corr_data)[,-1]
y = corr_data$Popularity
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
ResultMatrix <- c(abs(matrix(best_model$beta)))
Names <- colnames(x)
TopVariables <- data_frame(Names,ResultMatrix) %>% 
  arrange(desc(ResultMatrix)) %>% 
  filter(!grepl("Genre", Names)) %>% 
  top_n(2)
TopVariables

```




---
-These are the linear models of each genre that regress Popularity on all variables
-We have chosen to regress Popularity on all variables for every genre to maintain consistency, which explains why some genres do not show high significance for Energy and Danceability until less significant variables are ommitted
-This helps us confirm our results from Lasso: Energy and Danceability are the variabes that have the greatest contribution to the model of predicting Popularity 
-When comparing genres, we can see that there is a difference in importance of Energy/Danceability in predicting Popularity
-We can also see that there is significant variance in Popularity for songs with the same or very similar Energy/Danceability
---
```{r}
#############
# Alternative
#############
AlternativeModel <- lm(Popularity ~ .,data = AlternativeData)
summary(AlternativeModel)

effect_plot(AlternativeModel, pred = Energy, interval = TRUE, plot.points = TRUE, jitter = 0.05) +
  labs(title = "Energy vs. Popularity for Alternative Music")
effect_plot(AlternativeModel, pred = Danceability, interval = TRUE, plot.points = TRUE, jitter = 0.05) + 
  labs(title = "Danceability vs. Popularity for Alternative Music")


#############
# Country
#############
CountryModel <- lm(Popularity ~ .,data = CountryData)
summary(CountryModel)

### This plot shows the effect of chosen regressor (pred) on Popularity
effect_plot(CountryModel, pred = Energy, interval = TRUE, plot.points = TRUE, jitter = 0.05) +
  labs(title = "Energy vs. Popularity for Country Music")
effect_plot(CountryModel, pred = Danceability, interval = TRUE, plot.points = TRUE, jitter = 0.05) +
  labs(title = "Danceability vs. Popularity for Country Music")


#############
# Hip Hop
#############
HipHopModel <- lm(Popularity ~ .,data = Hip_HopData)
summary(HipHopModel)

### This plot shows the effect of chosen regressor (pred) on Popularity
effect_plot(HipHopModel, pred = Energy, interval = TRUE, plot.points = TRUE, jitter = 0.05) +
  labs(title = "Energy vs. Popularity for Hip Hop Music")
effect_plot(HipHopModel, pred = Danceability, interval = TRUE, plot.points = TRUE, jitter = 0.05) +
  labs(title = "Danceability vs. Popularity for Hip Hop Music")


#############
# Latin
#############
LatinModel <- lm(Popularity ~ .,data = LatinData)
summary(LatinModel)

### This plot shows the effect of chosen regressor (pred) on Popularity
effect_plot(LatinModel, pred = Energy, interval = TRUE, plot.points = TRUE, jitter = 0.05) +
  labs(title = "Energy vs. Popularity for Latin Music")
effect_plot(LatinModel, pred = Danceability, interval = TRUE, plot.points = TRUE, jitter = 0.05) +
  labs(title = "Danceability vs. Popularity for Latin Music")


#############
# Pop
#############
PopModel <- lm(Popularity ~ .,data = PopData)
summary(PopModel)

### This plot shows the effect of chosen regressor (pred) on Popularity
effect_plot(PopModel, pred = Energy, interval = TRUE, plot.points = TRUE, jitter = 0.05) +
  labs(title = "Energy vs. Popularity for Pop Music")
effect_plot(PopModel, pred = Danceability, interval = TRUE, plot.points = TRUE, jitter = 0.05) +
  labs(title = "Danceability vs. Popularity for Pop Music")


#############
# Rock
#############
RockModel <- lm(Popularity ~ .,data = RockData)
summary(RockModel)

### This plot shows the effect of chosen regressor (pred) on Popularity
effect_plot(RockModel, pred = Energy, interval = TRUE, plot.points = TRUE, jitter = 0.05) +
  labs(title = "Energy vs. Popularity for Rock Music")
effect_plot(RockModel, pred = Danceability, interval = TRUE, plot.points = TRUE, jitter = 0.05) +
  labs(title = "Danceability vs. Popularity for Rock Music")


```


---
Regressions to find if changing Danceability/Energy has a significant impact on changing Popularity
Using Double Selection Procedure for Robust confidence Intervals

---

```{r}

{
####################################
# DANCEABILITY EFFECT ON ALTERNATIVE
####################################

### Step 1
set.seed(1)
x = model.matrix(Popularity ~ ., data=AlternativeData)[,c(-1,-3)]
y = AlternativeData$Popularity
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
## None insignificant


#### Step 2
set.seed(1)
x = model.matrix(Danceability ~ ., data=AlternativeData)[,c(-1,-2)]
y = AlternativeData$Danceability
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# None insignificant

### Step 3
summary(AltModel <- lm(Popularity ~ Danceability + ., AlternativeData))
## p-value is greater than 0.05, so we can conclude that increasing danceability will not have a significant effect on popularity for Alternative Music

####################################
# ENERGY EFFECT ON ALTERNATIVE
####################################

### Step 1
set.seed(1)
x = model.matrix(Popularity ~ ., data=AlternativeData)[,c(-1,-4)]
y = AlternativeData$Popularity
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
## Acousticness, Instrumentalness, Tempo

#### Step 2
set.seed(1)
x = model.matrix(Energy ~ ., data=AlternativeData)[,c(-1,-2)]
y = AlternativeData$Energy
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# Audio_Mode

### Step 3
summary(AltModel <- lm(Popularity ~ Energy + ., AlternativeData))
## p-value is less than 0.05, so we can conclude that changing Energy DOES in fact have a significant
## impact on popularity for Alternative Music

####################################
# DANCEABILITY EFFECT ON COUNTRY
####################################

### Step 1
set.seed(1)
x = model.matrix(Popularity ~ ., data=CountryData)[,c(-1,-3)]
y = CountryData$Popularity
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# Liveness

### Step 2
set.seed(1)
x = model.matrix(Danceability ~ ., data=CountryData)[,c(-1,-2)]
y = CountryData$Danceability
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# Key

### Step 3
model_step_3 = glm(Popularity ~ . , data = CountryData)
summary(model_step_3)
## p-value is greater than 0.05, so we can conclude that changing Danceability does not have a significant impact on popularity for Country Music



####################################
# ENERGY EFFECT ON COUNTRY
####################################

### Step 1
set.seed(1)
x = model.matrix(Popularity ~ ., data=CountryData)[,c(-1,-4)]
y = CountryData$Popularity
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# None

### Step 2
set.seed(1)
x = model.matrix(Energy ~ ., data=CountryData)[,c(-1,-2)]
y = CountryData$Energy
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# None

### Step 3
model_step_3 = glm(Popularity ~ . , data = CountryData)
summary(model_step_3)
## p-value is less than 0.05, so we can conclude that changing Energy DOES in fact have a significant impact on popularity for Country Music

####################################
# DANCEABILITY EFFECT ON HIP HOP
####################################

### Step 1
set.seed(1)
x = model.matrix(Popularity ~ ., data=Hip_HopData)[,c(-1,-3)]
y = Hip_HopData$Popularity
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta

# Instrumentalness, Key, Liveness Speechiness, Valence 

#### Step 2
set.seed(1)
x = model.matrix(Danceability ~ ., data=Hip_HopData)[,c(-1,-2)]
y = Hip_HopData$Danceability
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# None


### Step 3
model_3 <- lm(Popularity ~., data = Hip_HopData)
summary(model_3)
## p-value is less than 0.05, so we can conclude that increasing Danceability could have a significant effect on popularity Hip Hop


####################################
# ENERGY EFFECT ON HIP HOP
####################################

### Step 1
set.seed(1)
x = model.matrix(Popularity ~ ., data=Hip_HopData)[,c(-1,-4)]
y = Hip_HopData$Popularity
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta

## All except Acousticness, Danceability and Tempo

#### Step 2
set.seed(1)
x = model.matrix(Energy ~ ., data=Hip_HopData)[,c(-1,-2)]
y = Hip_HopData$Energy
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta

# Speechiness, Tempo 


### Step 3
model_4 <- lm(Popularity ~ .-Speechiness, data = Hip_HopData)
summary(model_4)
# The p-value on the treatment, Energy, is very significant, it's less than 0.05. We can conclude that changing Energy will have a significant impact on Popularity


####################################
# DANCEABILITY EFFECT ON LATIN
####################################

### Step 1
set.seed(1)
x = model.matrix(Popularity ~ ., data=LatinData)[,c(-1,-3)]
y = LatinData$Popularity
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
## Energy, Liveness, Valence, Length


#### Step 2
set.seed(1)
x = model.matrix(Danceability ~ ., data=LatinData)[,c(-1,-2)]
y = LatinData$Danceability
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# None 

### Step 3
summary(LatinModel <- lm(Popularity ~ Danceability + ., LatinData))
## p-value is greater than 0.05, so we can conclude that increasing danceability will not have a significant effect on popularity for Latin Music


####################################
# ENERGY EFFECT ON LATIN
####################################

### Step 1
set.seed(1)
x = model.matrix(Popularity ~ ., data=LatinData)[,c(-1,-4)]
y = LatinData$Popularity
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
## Liveness, Valence, Length


#### Step 2
set.seed(1)
x = model.matrix(Energy ~ ., data=LatinData)[,c(-1,-2)]
y = LatinData$Energy
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# Key

### Step 3
summary(LatinModel <- lm(Popularity ~ Energy + ., LatinData))
## p-value is less than 0.05, so we can conclude that changing Energy DOES in fact have a significant impact on popularity for Latin



####################################
# DANCEABILITY EFFECT ON POP
####################################

### Step 1
set.seed(1)
x = model.matrix(Popularity ~ ., data=PopData)[,c(-1,-3)]
y = PopData$Popularity
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# Key, Liveness, Loudness, Tempo, Audio_Valence

### Step 2
set.seed(1)
x = model.matrix(Danceability ~ ., data=PopData)[,c(-1,-2)]
y = PopData$Danceability
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# None

### Step 3
model_step_3 = glm(Popularity ~ ., data = PopData)
summary(model_step_3)
## p-value is less than 0.05, so we can conclude that changing Danceability DOES in fact have a significant impact on popularity for Pop



####################################
# ENERGY EFFECT ON POP
####################################

### Step 1  
set.seed(1)
x = model.matrix(Popularity ~ ., data=PopData)[,c(-1,-4)]
y = PopData$Popularity
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# Key, Liveness, Loudness, Tempo

### Step 2
set.seed(1)
x = model.matrix(Energy ~ ., data=PopData)[,c(-1,-2)]
y = PopData$Energy
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# Key

### Step 3
model_step_3 = glm(Popularity ~ .-Key, data = PopData)
summary(model_step_3)
## p-value is greater than 0.05, so we can conclude that increasing Energy will not have a significant effect on popularity for Pop Music


####################################
# DANCEABILITY EFFECT ON ROCK
####################################

### Step 1
set.seed(1)
x = model.matrix(Popularity ~ ., data=RockData)[,c(-1,-3)]
y = RockData$Popularity
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
## Energy, Key, Liveness, Audio, Speechiness, Valence

### Step 2
set.seed(1)
x = model.matrix(Danceability ~ ., data=RockData)[,c(-1,-2)]
y = RockData$Danceability
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# None

### Step 3
summary(RockModel <- lm(Popularity ~ ., RockData))
## p-value is greater than 0.05, so we can conclude that increasing Danceability will not have a significant effect on popularity for Rock Music



####################################
# ENERGY EFFECT ON ROCK
####################################

### Step 1
set.seed(1)
x = model.matrix(Popularity ~ ., data=RockData)[,c(-1,-4)]
y = RockData$Popularity
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# Danceability, Key, Liveness, Mode, Speechiness, Valence

### Step 2
set.seed(1)
x = model.matrix(Energy ~ ., data=RockData)[,c(-1,-2)]
y = RockData$Energy
cv.model = cv.glmnet(x, y, alpha=1)
optimal_lambda = cv.model$lambda.min
optimal_lambda
plot(cv.model)
lasso <- glmnet(x, y)
summary(lasso)
best_model <- glmnet(x, y, alpha= 1, lambda = optimal_lambda)
best_model$beta
# Key

### Step 3
summary(AltModel <- lm(Popularity ~ .-Key, RockData))
## p-value is greater than 0.05, so we can conclude that increasing Energy will not have a significant effect on popularity for Rock Music
}

```

---
Putting the results of Double Selection in a table
Our table tells us, for each genre, if changing the variable will have a significant effect on Popularity
---
```{r}
# In this table,"Yes" means that changing the attribute will have an effect on Popularity for that genre. "No" means that changing the attribute has a low significance in affecting Popularity.
Genre <- c("Alternative", "Country", "Hip Hop", "Latin", "Pop", "Rock")
Danceability <- c("No", "No", "Yes", "No", "Yes", "No")
Energy <- c("Yes", "Yes", "Yes", "Yes", "No", "No")

Results <- as.data.frame(cbind(Genre, Danceability, Energy))
Results

```

